Motorcycle Acceleration example

### 2018-11-06 analysis/motorcycle.Rmd

An illustration of "smoothing via adaptive shrinkage" (SMASH) applied to the
Motorcycle Accident data. This implements the "illustrative application"
presented in Sec. 5.1 of the manuscript.

@@

Set up environment
------------------

Load the MASS, scales, wavethresh, EbayesThresh and smashr
packages. The MASS package is loaded only for the Motorcycle
Accident data. Some additional functions are defined in
`functions.motorcycle.R`.

```{r load-pkgs, message=FALSE}
library(MASS)
library(lattice)
library(smashr)
library(scales)
library(wavethresh)
library(EbayesThresh)
source("../code/motorcycle.functions.R")
```

@@

Apply SMASH (assuming with equal variances) to the Motorcycle Accident
data set.

@@

Apply TI thresholding to the Motorcycle Accident data
---------------------------------------------------

>>>>

This is an illustration of "smoothing via adaptive shrinkage" (SMASH)
applied to the Motorcycle Accident data. This implements the
"illustrative application" presented in Sec. 5.1 of the manuscript.

@@

Initial setup instructions
--------------------------

To run this example on your own computer, please follow these setup
instructions. These instructions assume you already have R and/or
RStudio installed on your computer.

Download or clone the [git repository][smash-github] on your computer.

Launch R, and change the working directory to be the "analysis" folder
inside your local copy of the git repository.

Install the devtools, wavethresh and EbayesThresh packages used here
and in the code below:

```{r install-pkgs-1, eval=FALSE}
install.packages(c("devtools","wavethresh","EbayesThresh"))
```

Finally, install the ashr and smashr packages from GitHub:

```{r install-pkgs-2, eval=FALSE}
library(devtools)
install_github("stephens999/ashr",upgrade_dependencies = FALSE)
install_github("stephenslab/smashr",upgrade_dependencies = FALSE)
```

See the "Session Info" at the bottom for the versions of the software
and R packages that were used to generate the results shown below.

Set up R environment
--------------------

Load the MASS, wavethresh, EbayesThresh and smashr packages. The MASS
package is loaded only for the Motorcycle Accident data. Some
additional functions are defined in `functions.motorcycle.R`.

```{r load-pkgs, message=FALSE}
library(MASS)
library(lattice)
library(smashr)
library(wavethresh)
library(EbayesThresh)
source("../code/motorcycle.functions.R")
```

Note that the MASS and lattice packages are included in most standard
R installations.

@@

Apply SMASH (assuming equal variances) to the Motorcycle Accident data
set.

@@

Apply TI thresholding to the Motorcycle Accident data
-----------------------------------------------------
